\documentclass[x11names,parskip=half,american]{bewerbung}
\LoadLetterOptions{tastyFriedLiver}
\addbibresource{tflCvReferences.bib}
\usepackage{AlegreyaSans}
\usepackage{babel}
\usepackage{Alegreya}
\usepackage{hyperref}
\newcommand{\lang}[1]{\texttt{#1}}

\begin{document}
\makecover[
ambitious\\
knowledgeable\\
trustworthy
]
\setkomavar{subject}{job application}
\setkomavar{title}{your search is over}
\begin{letter}{Dagobert Duck\\
		Human Ressources\\
	Duckburg}
	\opening{Dear Human Ressources Guys,}

	seems you are looking for a reliable person to run the
	local nuclear power plant. I think your search will be
	over after you invited me for an interview. I am
	 everything you need and i am willing to contribute my
	knowledge and strength to the company. 

	I make a hell of a potato salad, i'll prove it at
	the next company picnic.

	I'll enclose some of my previous activities.

	\closing{Best regards}
\encl{zeugnis, Photo}
\end{letter}


\cvsymbols
\begin{cv}
	\cvsec{Scholarly Stuff}
	\cvdate{2007}{Duckburg High School}[Abitur-High School
	Diploma]
	\cvdate{2007-10-1012-12}{University of
	Shelbyville}[Thesis: \citetitle{thesis:ddd}]
	\cvsec{Achievements}
	\cvdate{2013-11-01}{The naked man}[ Demonstrating nude in
	front of the \emph{Reichstag}]
	\cvdate{2007-10 - 2014}{Duff Man}[ making promotions for Duff, the best beer a man can find ]
	\cvdate{2013-10-25}{Best day of my life}[I married the
	girl of my dreams, Patty Mayonaise]
	\cvsec{Experience}
	\begin{cvlist}
	\item [Office] Fluent with Microsoft Office products like
		Word, Excel and all the other crap
	\item [Operating systems] Good knowledge of Microsoft
		Windows for compatibility reasons, fluent wuth
		\texttt{unix}oide systems
	\item [Languages] I can speak english, german, a little
		bit french. Though i cannot speak it, i know the
		greek, russian and korean script. 
	\item [\faCode] For every purpose something special:
		\lang{perl}, \lang{LaTeX}, \lang{awk}, \lang{sed},
		and a little bit of \lang{R}, \lang{Matlab}
		\\I cannot use \lang{pyhton} though, i have
		\emph{AngstVorSchlangen}
	\item [multitalent] washing the dishes, repair the table,
		set up the TV, changing diapers, securing a
		building, getting things done.\\ What needs to be done will be done. 
	\end{cvlist}
	\nocite{*}
	\printbibliography[heading=cvRef]
\end{cv}
\end{document}

%TODO: fix dates to word (somehow) with biblatex.

